---
title: "lab1-1-review-gavinemartinez"
output: html_document
date: "2023-04-06"
---
```{r libraries}
library(here)
library(tidyverse)
```

**Checking Normality**  
```{r dataset}
OscarsDemo = read.csv(here('Oscars-demographics-DFE.csv'))
```

In this section, you will use a **Q-Q Plot** to check if a vector of values `x` comes from a Normal distribution.  
The approach is to randomly generate a new vector `y` from a Normal distribution with the same mean and standard deviation as `x`, 
then to create a Q-Q plot of `x` and `y`.
*(Note: A typical Normal Q-Q plot uses theoretical quantiles instead of randomly generated values.  We're taking a bit of a shortcut
in this assignment.)*

```{r}
#x is the year_of_award variable
x = OscarsDemo$year_of_award
len_x = length(x)
mean_x = mean(x)
sd_x = sd(x)

#y is a randomly generated vector of equal length as x, with a mean and sd identical to x.
y = rnorm(len_x, mean_x, sd_x)

#sort in decreasing order
x = sort(x, decreasing = T)
y = sort(y, decreasing = T)

plot(x,y, main = 'QQ-plot for x')
abline(0,1)

```







