---
title: "lab1-1-review-gavinemartinez"
output: html_document
date: "2023-04-06"
---
```{r libraries}
library(here)
library(tidyverse)
```

**Checking Normality**  
```{r dataset}
OscarsDemo = read.csv(here('Oscars-demographics-DFE.csv'))
```

A Q-Q (Quantile-Quantile) Plot is a way of checking if two collections of observations come from the same distribution.

The steps are as follows:

1. Take two vectors of the same length, `x` and `y`.
```{r}
x = 
```


2. Put the vectors in order from largest to smallest.

3. Pair the ordered vectors up, so that the smallest value of `x` is paired with the smallest value of `y`, and so on.

4. Make a scatterplot of the ordered pairs.  


If the points in the scatterplot fall on a straight line, with intercept 0 and slope 1, 
this suggests that `x` and `y` are sampled from the same distribution.


In this section, you will use a **Q-Q Plot** to check if a vector of values `x` comes from a Normal distribution.  
The approach is to randomly generate a new vector `y` from a Normal distribution with the same mean and standard deviation as `x`, 
then to create a Q-Q plot of `x` and `y`.
*(Note: A typical Normal Q-Q plot uses theoretical quantiles instead of randomly generated values.  We're taking a bit of a shortcut
in this assignment.)*






