---
title: "Part 2"
output: html_document
date: "2023-04-06"
---
## Data
```{r}
library(here)
OscarsDemo = read.csv(here("Oscars-demographics-DFE.csv"))
```

1. Which movie(s) won the most unique "Big 5" awards?
```{r}
#dplyr
library(dplyr)
unique_awards <- OscarsDemo %>%
  group_by(movie) %>%
  summarize(num_awards = n_distinct(award))

#base R
unique_awards <- tapply(OscarsDemo$award, OscarsDemo$movie, function(x) length(unique(x)))
unique_awards <- data.frame(movie = names(unique_awards), num_awards = unique_awards, row.names = NULL)


```
**By looking at the data set and clicking the header of the column for num_awards, we can see that there are quite a few movies that recieved 3 unique awards, some of them being A StreetCar Named Desire and Cabaret.**  

2. Of all actresses who have won the Best Actress award, what are is the most common first name?
```{r}
# base R
library(stringr)
OSCAR2 = OscarsDemo[OscarsDemo$award == 'Best Actress',]
fullnames = unique(OSCAR2$person)
first_names <- str_extract(fullnames, "\\w+")
names(sort(table(first_names), decreasing = TRUE))[1]

# dplyr
OscarsDemo2  = OscarsDemo %>%
  select(award, person) %>%
  filter(award == 'Best Actress')%>%
  distinct(person) %>%
  mutate(firstname = str_extract(person, "\\w+")) %>%
  group_by(firstname) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  slice(1) %>%
  pull(firstname)
OscarsDemo2
  
```
**The most common first name among all actresses who have won Best Actress is Helen.**  

3. What US State, or non-US country, has produced the most Oscar winners (for the awards in this dataset)?  
```{r}
states = str_extract(OscarsDemo$birthplace, '\\b[^,]+$')
names(sort(table(states), decreasing = T))[1]

OscarsDemo3 = OscarsDemo %>%
  mutate(states = str_extract(birthplace, '\\b[^,]+$')) %>%
  group_by(states) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  slice(1) %>%
  pull(states)
OscarsDemo3  
```
**For he awards in this dataset, England has produced the most Oscar winners.**


